### 2016-11-01 ms/ms.tex
made the .bib changes

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what would be expected from preferential
attachment. With a preferential attachment process, we expect that the
most persistent and high degree species would remain stable in the
network core during assembly
\citep{barabasi1999emergence}. Surprisingly, however, we encountered
the opposite pattern. For example, the four most ubiquitous species in
our study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module they were a member in across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be better able to exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also be the most persistent \citep[in ant-plant
mutualisms, ][]{diaz2010changes}. More persistent species usually have
longer phenologies, so they can visit many different flowers,
resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{macleod2016measuring, gomez2006ecological,
  waser1996generalization}. Thus given the opportunity and ability to
use different resources, species will often change their network
positions \citep{macleod2016measuring}.

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/scheme.pdf}
  \caption{Diagram illustrating the analysis to examine the temporal
    turnover of interactions weighted based on their similarity. A, B
    and C are animal species, and Ps are plant species. The dendrogram
    depicts the interaction similarity across years based on the
    number of shared constituent species.}
  \label{fig:methods}
\end{figure}
\clearpage

>>>>

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what would be expected from preferential
attachment. With a preferential attachment process, we expect that the
most persistent and high degree species would remain stable in the
network core during assembly
\citep{barabasi1999emergence}. Surprisingly, however, we encountered
the opposite pattern. For example, the four most ubiquitous species in
our study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module they were a member in across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be better able to exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also be the most persistent \citep[in ant-plant
mutualisms, ][]{diaz2010changes}. More persistent species usually have
longer phenologies, so they can visit many different flowers,
resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{macleod2016measuring, gomez2006ecological,
  Waser1996}. Thus given the opportunity and ability to
use different resources, species will often change their network
positions \citep{macleod2016measuring}.

@@

\clearpage
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/scheme.pdf}
  \caption{Diagram illustrating the analysis to examine the temporal
    turnover of interactions weighted based on their similarity. A, B
    and C are animal species, and Ps are plant species. The dendrogram
    depicts the interaction similarity across years based on the
    number of shared constituent species.}
  \label{fig:methods}
\end{figure}
\clearpage
